Analysis of split plot design using MCMCglmm

### 2018-04-12 README.Rmd
Correct link for docker image installation in README
Update README

## Research compendium for a report on the effects of using alternate wetting and drying irrigation techniques on sheath blight disease in rice paddies.

@@

    docker run -dp 8787:8787 adamhsparks/rice.awd.pests

>>>>

## Research compendium for a report on the effects of using alternate wetting and drying irrigation techniques and nitrogen rates on sheath blight disease in rice paddies.

@@

    docker run -dp 8787:8787 adamhsparks/rice_awd_pests
